---
title: "Question 1"
---


##### (a) Use bootstrap to construct a 95\% confidence interval for the coefficient determination $R^2$ of the file "data.csv" when `y` is regressed on `x`.

Remark: use either classical bootstrap or bootstrap percentile confidence interval.



##### (b) There are 1000 rows of observations in "data.csv". Imagine that the file is split into 10 parts. Write a function `get_data` to read each part separately (i.e., given the value `i` between 1 and 10, write a function which reads the `(i-1) * 100 + 1` to `i * 100` rows directly from the file)


```{r}
get_data <- function(i) {

}
```


##### (c) Write a function `get_coef` that returns the coefficient of determination $R^2$ when `y` is regressed on `x` using weighted least square with weights `w`'s. 
(`w` has the same length as `x` and `y`)

Remark: you might either calculate it manually or by using base R functions.


```{r}
get_coef <- function(x, y, w) {

}
```

##### (d) Use the bag of little bootstraps algorithm (with 10 subsamples) to estimate a 95\% conficence interval for the $R^2$ of the file `data.csv`.

Hints: Use `furrr` or otherwise to speed up computation by utilizing more than one core.
