---
title: "Question 2"
---

In this question, you would use the `reticulate` package to write some python code.

First make sure that you have `reticulate` and miniconda installed.

```{r}
library(reticulate)
```

Install `miniconda` if you haven't.
```{r, eval = FALSE}
install_miniconda()

```
Tell `reticulate` to use `miniconda`.
```{r}
use_miniconda(required = TRUE)
```


##### (a) Write a function `kendall_a` in python which caclulates Kendall Tau coorelation. Suppose `x` and `y` are two numpy arrays of the same length. For simplicity, assume that there are no missing values and ties (Tau-a coefficient).

(Do not use functions such as `scipy.stats.kendalltau` or `pandas.DataFrame.corr`, write your own function!)


```{python}
def kendall_a(x, y):
  
  return tau

```

```{python}
import numpy as np
n = 10000
x = np.random.rand(n)
y = np.random.rand(n)
kendall_a(x, y)
```

```{r}
n <- 10000
# R's array will be casted as Python's numpy array
x <- as.array(runif(n))
y <- as.array(runif(n))
py$kendall_a(x, y)
cor(x, y, method = "kendall")
```

##### (b) Recall part (a), but `x` and `y` may have ties now. (Tau-b coeffient)

Hint: `np.unique(x, return_counts=True)`

```{python}
def kendall_b(x, y):
  
  return tau
  
```

```{python}
import numpy as np
from math import floor
n = 10000
x = np.random.choice(floor(n * 0.9), n)
y = np.random.choice(floor(n * 0.9), n)
kendall_b(x, y)
```

```{r}
n <- 10000
# R's array will be casted as Python's numpy array
x <- as.array(sample.int(floor(n * 0.9), n, replace = TRUE))
y <- as.array(sample.int(floor(n * 0.9), n, replace = TRUE))
py$kendall_b(x, y)
cor(x, y, method = "kendall")
```
