---
title: "Question 3"
---

In this question, you are going to use `keras` to build a neural network to predict wheather an email of spam or not.


```{r}
library(reticulate)
library(tidyverse)
library(keras)
```

If you haven't done it yet, you would need to install the python package `keras`. 
We are going to install it to the miniconda environment `r-tensorflow`. 
(It requires you to install `miniconda` as indicated in q1.)


```{r, eval = FALSE}
install_keras("conda", conda = reticulate:::miniconda_conda(), envname = "r-tensorflow")
```

To use the environment. (You might need to restart the R session before running the below code.)
```{r}
use_miniconda("r-tensorflow", required = TRUE)
```

The data is from the package `kernlab`

```{r}
library(rsample)
library(kernlab)
data(spam)
```
Use `?spam` to see the documentation of the dataset.

We first randomly split the data into training and testing set

```{r}
set.seed(141)
nspam <- 1813
nham <- 2788
test <- c(sample(1:nspam, floor(nspam * 0.1)), sample(nspam + 1:nham, floor(nham * 0.1)))
spam_train <- spam[-test, ]
spam_test <- spam[test, ]
```



PS: You could use either python or R to answer the following questions.


###### (a) Build a neural network on the variable `type` of the `spam_train` dataset.

Hint: It is sufficient to use one hidden dense layer and one dropout layer.




###### (b) Predict the email type for the records in `spam_test`. What is the misclassification rate?
